\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{hyperref}
\title{today's thoughts}
\begin{document}
\maketitle
\section{problems}
\begin{itemize}
    \item min jsts: why can't i. i can, i will but i think it's not effective.
    \item i came back thinking too fast. i have to setup a limit first.
    \item I need to alternate also, alternating is broken.
    \item I had another problem: the found subjects of yesterday. there is no step, task, plan to learn them
    \item Now what?
    \begin{itemize}
        \item I can stick to after minis choice which is alternation of update personal docs and summarizing
        \item I can make the current activity recurrent since it already is. diary freewriting or what now answering.
        \item I can brainstorm head caught problems and choose one.
        \item I want to get a job fast to be able to start my separation project. This is i know.
        \begin{itemize}
            \item to get that, do i need to implement different frequencies tasks?
            \item Why can't i think, where there are no thoughts in my head ? is it because of the noise?
            \item in order to get a job and reduce skillset gap, do i need different frequencies tasks of do i need to add tasks in job seazrch category?
            \item If i keep doing one small task per day in job search, i won't progress
            \item should my trunc problem become progression, or reaching goals
            \item I don't remember why i ditched different frequencies working
            \item must be that, in fact, switching the activity every 20 minutes created unnecessary brainfog context switch without finishing anything concrete even smallest.
            \item Do i need to return to frequencies based tasks to get a job and learn technical skills? is nt there another solution for organizing job search and skillset gap reducing? is there only recurrent tasks approach? Don't I have another alternative? Is it the only way to combine ideas clarity maintenance, admin and expenses maintenance, and job search and technical skills progression?
            \item chatgpt: time blocks allocation, kanban org, weekly accomplishments planning
            \item crossing rahp requires frequencies (déjà i am failing to cross every 4h)
            \item the tasks should contain self care: i can't deep work without eating some nutrients, cleaning my room, showering. these are recurrent.
        \end{itemize}
    \end{itemize}
\end{itemize}
For fucks sake, I have another idea (thinking, problem) before executing anything:
\begin{itemize}
    \item How to create frequent tasks without breaking finishing minimums in important categories.
    \item minimal rahp is to cross /4h
    \item minimal self care is anything from the list or eating 6 nutrients.
    \item minimal expad is progress or postpone except three (or wishlist update)
    \item minimal thinking is writing
    \item Even minimal accomplishements per category requires ordering of tasks and frequencies.
    \item I am only afraid of prioritizing job search and technical skills too much.
\end{itemize}
If i have urgency to make job search and/or TSL a priority, why don't i just change the after minis selection instead of quadri-change my method of tasks organization?
Should i solve the problem of not sticking to selected after minis if i should change the after minis selection instead of frequencies implementation?
I meaning why am i leaving problems unsolved for example the failure to minimums. 
What if my problems right now is failure to finish a logical finish.
What if it don't matter what method i use to organize my tasks and answer what to do now if I don't learn from mistakes, aim to get better.
I am tired from thinking. What should i do now?
First I identify, mark done and recurrencify current task: I am thinking and writing. What is thinking? i am just freewriting in the hope of identifying most important problem and a solution.
Simple recurrent tasks help me like i can clean my files, i can clean my room, all   are recurrents.
\section{Now what}
Even though i create thre frequencies based tasks list, i still ask this question.
\end{document}