\documentclass{article}
\title{Technical skills learning}
\usepackage{hyperref}
\begin{document}
\maketitle
\section{Introduction} Technical skills learning is not a professional skill despite its' goal. This skill's purpose it to allow you to get a job by learning skills useful for an employer. Research questions about selected technical skill. Questions can be generated after
\begin{itemize}
	\item consuming a source 
    \item reading source code
    \item reading existent notes 
    \item building (practising skills)
    \item starting to answer 
\end{itemize}
A material's decomposition is a suggestion to organize your own notes, also code decomposition but best is skill decomposition
\section{Technical skill selection analysis}
\subsection{First} is asp.net webapi development since it's the most wanted c\# library.
\begin{itemize}
	\item I refused a java developer position. Why do I want C\# and nothing else?
	\item Are there skills more wanted than asp.net? like advanced git, advanced OOP, systems administration, CI/CD, Design patterns, Software architecture, frontend in angular/react, TDD.
\end{itemize}
\section{Next skills}
\begin{itemize}
	\item C\#
\item design patterns \& software architecture
\item entity
\item T-SQL
\item languages
\item CDCI : abp? yaml?
\item SQL
\item NoSQL
\item Powershell
\item Git
\item Azure 
\end{itemize}
\section{Hierarchical professional project options selection}
\begin{itemize}
	\item Save alot and retire
	\begin{itemize}
		\item Win the lottery/inherit money (will not happen)
		\item  Sell a startup (will not happen)
		\item Build investment portfolio (no money)
	\end{itemize}
	\item Get a job
	\begin{itemize}
		\item Not engineering
		\item engineering
		\begin{itemize}
			\item None IT engineering
			\item IT engineering
			\begin{itemize}
				\item Intelligence: Data science, Machine learning, AI
				\item Management: Project Delivery, PO, architecture
				\item administration: database administration, systems administration, cloud administration, deployment administration
				\item development: frontend apps, backend apps, PC apps, mobile apps, ERP apps, immersive apps, niches apps
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\item Get small contracts
	\item Get back to school
\end{itemize}
\section{competition watching}
\begin{itemize}
	\item \href{https://www.doyoubuzz.com/fr/p/lastRegistered}{doyoubuzz}
	\item \href{https://www.google.com/search?q=intitle:cv+filetype:pdf&tbs=qdr:m}{google}
	\item \href{https://www.pdfsearchtool.com/#gsc.tab=0&gsc.q=cv%20d%C3%A9veloppeur&gsc.sort=date&gsc.page=3}{pdfsearchtool}
	\item \href{linkedin.com}{linkedin}
\end{itemize}
\end{document}