\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\title{Day accomplishments organization}
\begin{document}
\maketitle
\section{Introduction}
I made the decision that my dw goal is a certain amount of time. I forgot why I changed back to minimal tasks per dw category. I forget why i have minimal progression goal per category. I feel that it's not working anymore. I forgot what other alternatives of DAA i have. Why has DAA moved to electronic format? If true, does every current DAA maintain a solution and prevent a recurring problem? What skill is this? Can i decompose it?
\section{Imported notes}
Never go shopping if it's not planned. Day Planning is a maintenance task. It prevents overdoing one task and neglecting others. Never do a day plan not based on top of quarterly refuses because it's the only start to prevent DTSBF. Other steps are to add refuse drink coffee (it effects you 24h), refuse salt it gives you nocturia, r eat none planned items (low glucids, low lipids, low prep, low cost). A preplanned tasks of deep work don't allow me get back where i stopped if i get interrupted or if i get a job
Never delete this. Refactor it if you want but never delete. Daily Aiming for minimums accomplishments per category of tasks allows you to
\begin{itemize}
    \item have a foundation for anything you do even if you don't do anything
    \item prevent problems cumulation in a life domains
    \item have a resume point when you get interrupted
\end{itemize}
Usable categories of DAA minis are
\begin{itemize}
    \item Self care
    \item RAHP
    \item problems prev and solving
    \item Career building
    \item exp and admin expad
    \item after minis for when time allows it. 
\end{itemize}  
\end{document}
