\documentclass{article}
\title{Health}
\begin{document}
\maketitle
Daytime sleepiness and brainfog don't only come from addictions and absent self care.
\section{Addictions}
An addiction is a practice or a consumption that a person can't stop despite harms. My personal definition is a harmful pleasure. At first, it starts a pleasure but it transforms into a pseudo need in a way that is painful to resist and hard to stop. The problem with quitting addictions is they don't have a finish time like actions and tasks. Therefore, in order to quit an addiction, you need to divide your day into four hours and consider every sober slot a separate accomplishment. Watching series is bad because among others it makes you think of them instead of your current task. I regret that I ate unauthorized foods. I am brainfogged again.
•	I am not progressing on addictions quitting
•	Watching too much series makes you think of them instead of what to do now
•	I keep forgetting that caffeine in the morning brings after noon dtsbf and prevents u from sleep @ 23:00
•	I think I need sunset to sunrise fasts (not just food) (nocturia, dtsbf, self restrain practice)
•	I have caffeine addiction. Caffeine reduces the quality of my thinking.

\section{Self care}
Why self care
- Being thirsty makes you tired and fogged
- faut trouver none screen before bed activity to sleep better
- what is triptophane
How to take a shower
put clean clothes only
Tasks of self care
take a shower
teeth routine brush floss, wash
clothes clean dry fold change
food buy prep dishes
pa cardio strech strenght
how to do dishes
how to execute admin tasks
•	I have many lack-of-self-care-consequence problems
o	I am still sick
o	I still get new sicknesses
o	I score high on premature death
•	I hate PA because overweight and smiking
•	Update eating plan is important but not in my recurrent tasks

\end{document}