\documentclass{article}
\title{Technical skills learning}
\usepackage{hyperref}
\begin{document}
\maketitle
\section{Introduction} Technical skills learning is not a professional skill despite its' goal. This skill's purpose it to allow you to get a job by learning skills useful for an employer. You need to research questions about selected technical skill. Questions can be generated 
\begin{itemize}
	\item after consuming a source of knowledge or 
    \item examining technical products ( aka source code)
    \item Maybe existent notes reading
    \item Or building (practising skills)
    \item or maybe by starting to answer 
\end{itemize}
A material's decomposition is a suggestion to organize your own notes, also code decomposition but best is skill decomposition
\section{Technical skill selection analysis}
\subsection{First} is asp.net webapi development since it's the most wanted c\# library.
\begin{itemize}
	\item I have my doubts on this. I used suggested a java developer position but i refused it. Was i in a position to refuse?
	\item I failed to introduce the transferable technical skills idea. I mean what if there are skills that are more wanted than asp.net, like advanced git, advanced OOP, systems administration, CI/CD, Design patters, Software architecture, frontend in angular/react. These skills are wanted after asp.net, they are also wanted when the backend is not c\#.
\end{itemize}
\section{Next skills}
\begin{itemize}
	\item C\#
\item design patterns \& software architecture
\item entity
\item T-SQL
\item languages
\item CDCI : abp? yaml?
\item winforms
\item wpf
\item SQL
\item NoSQL
\item Bash
\item Shell
\item Powershell
\item Git
\item Azure 
\end{itemize}
\section{Hierarchical professional project options selection}
\begin{itemize}
	\item Save alot and retire
	\begin{itemize}
		\item Win the lottery/inherit money (will definitely not happen)
		\item  Sell a startup (will most likely not happen)
		\item Build investment portfolio (no money, too slow, too risky)
	\end{itemize}
	\item Get a job
	\begin{itemize}
		\item Not engineering
		\item engineering
		\begin{itemize}
			\item None IT engineering
			\item IT engineering
			\begin{itemize}
				\item Intelligence: Data science, Machine learning, AI
				\item Management: Project Delivery, PO, architecture
				\item administration: database administration, systems administration, cloud administration, deployment administration
				\item development: frontend apps, backend apps, PC apps, mobile apps, ERP apps, immersive apps, niches apps
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\item Get small contracts
	\item Get back to school
\end{itemize}
\section{competition watching}
\begin{itemize}
	\item \href{https://www.doyoubuzz.com/fr/p/lastRegistered}{doyoubuzz}
	\item \href{https://www.google.com/search?q=intitle:cv+filetype:pdf&tbs=qdr:m}{google}
	\item \href{https://www.pdfsearchtool.com/#gsc.tab=0&gsc.q=cv%20d%C3%A9veloppeur&gsc.sort=date&gsc.page=3}{pdfsearchtool}
	\item \href{linkedin.com}{linkedin}
\end{itemize}
\end{document}