\documentclass{article}
\title{feeling lost again}
\begin{document}
\maketitle
The fuck again. I have too many things to finish and i am not finishing anything. I have too many problems and i am not solving anything.
\section{Problem decomposition}
I think that feeling lost comes from the combination of the following problems:
\begin{itemize}
    \item Not finishing tasks: i don't have a list of logical finishes.
    \item too many recurrent tasks, aka, your DAA list is too long.
    \item Unordered recurrent tasks: i have to chose too frequently
    \item Not solving problems: did you recently solve a list of problems not matter the size or importance?
    \item too many problems: all reviews problems list is too long.
    \item Unordered problems: everytime, i have to chose again.
\end{itemize}
\section{Feeling lost detection problems}
\begin{itemize}
    \item I don't have a recurrent task to check symptoms of imminent lost feeling.
    \item I don't have a logging solution to track the reoccurence.
    \item I don't have prevention tasks.
\end{itemize}
\section{Potential Causes}
\begin{itemize}
    \item Wanting rotation instead of any.
    \item Stopped trying to cross
    \item Forgot why min DAA per category
    \item no morning routine to push start crossings
    \item no step of brainstorming tasks @ dw start
    \item free roaming thinking cause me to make decisions i forget
    \item is it a fake feeling? No.
    \item lack of control on my environment
    \item not progressing on a strategic plan to live better.
\end{itemize}
\section{Now what}
This problem is not solved yet.
\end{document}