\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\title{How to get back to updating RCATs}
\begin{document}
\maketitle
    I decided that the most important problem is returning to work according to RCAT. because no one will tell what i need to do. But i should watch out from two things:
    \begin{itemize}
        \item time orientation tasks instead of logical finishes.
        \item thinking branch forgetting.
        \item There was i think the following unsolved problem: if my final goal is to deep work 12h/day, is it healthy, is it possible, most importantly, why my day goals are different from the trunc problem. (trunc problem has root causes). If my day goal is crossing at least one accomplishment per category of daily tasks. why is nt this the trunc problem.
    \end{itemize}
    This is not a problem. This The problem is the symptoms and consequences of working without 3 liner RCAT branches:
    \begin{itemize}
        \item Loss feeling: i don't know what i want and what i need to do to get there.
        \item No priortizing of deepest causes solving on top of other tasks.
        \item 
    \end{itemize}
\subsection{Conlusion of returning to RCAT} deep work 10h/day is one aimed accomplishment among others. Its failure is the problem. Maybe my measurable goal changed to 2h/q which i failed. I have other problems not just failing daily aimed accomplishements like : job search tasks are inefficient. i don't have technical skills. i have dtsbf. I still catch new sicknesses. I have domestic violance. I can't move out. 
Linking them might be good. But i can solve problems without linking everything. Also i trying to solve everything might be the definition of too many goals. Okay this analysis must be separated for later revision.
\section{After conclusion opinion}
This is an example of recreating my organization from scratch. Concidentally, i was interrupted before recreating my organization. How can i minimally change my organization in order to have recurrent tasks.
\begin{itemize}
    \item Does my problem becomes that my job search tasks don't have the same importance?
    \item I have another problem. what the fuck am i doing? I don't want to think indefinitly and time based?
    \item This is a better problem. I am spending time writing thoughts with no finish aim. i will spend the whole if say if i start with thinking activity.
    \begin{itemize}
        \item a number of updated thinking documents.
        \item a number of finished problems analysis. A problem analysis is a document.
        \item a number of goals changes? this don't guarantee clarity improving.
    \end{itemize}
\end{itemize}
\section{decision}
Firslty, updating a number of documents is important since it improves my understanding of the subjects. This can be done by creating a repository and watching number of updates. Secondly, I should stop reading long formats since day goal depends on time based finishes.
So, i need to install github for my notes. Secondly, i need a pipeline for readings. Thirdly, i need to update my thinking goals.
\begin{itemize}
    \item won't the number of updates cause to seek smallest improvement to increase number of documents?
\end{itemize}
\begin{itemize}
    \item \item if i can return to RCAT, i will be able to solve problems and reach goals .
    \item but i can't do that. why?
    \begin{itemize}
        \item firstly, i fucking hate frequent change of method of tasks organization
        \item in what branch will you put (review, plan, learn) category? proactive problem solving/lifestyle improving.
        \item is this another cause of failing deep work
        \item is this a cause of failing one of deep work root causes
        \item is this the soil of the tree, aka if no proactive problem solving/lifestyle improving, there is no RCAT?
        \item if this is node, do i have root causes of failing to prevent and solve problems?
        \item Just by asking chatgpt and checking his answers, i have found out that i lack important skills practicing and knowledge like: executive functioning, self regulation, 
        \item okay i found out that inefficient problem solving and preventing have causes but what does it cause in my unified rcat.
        \item it does not have to be in one rcat. i can grow a second tree now: a meta tree.
        \item The problem with starting a second tree is that i don't know how to prioritize tasks anymore.
        \item When i made no self care and rahp causing dtsbf wich causes failure to deep work i struggled to prioritize dtsbf vs FI. logging helped prioritized.
        \item how can i find the priority between dw and proactive living? is proactive living a cross rcat nodes problem
        \item i had a root cause analysis tree wich helped me prioritize tasks. i fail to deep work enough because i have family interruptions because i can't move out because i overspend and because i don't have job because i don't have technical skills. i have another branch: i don't deep work enough because i have frequent daytime sleepiness and  brainfog because i have too much addictions and i don't self care. logging the causes of failing deep work allowed to understand that family interruptions is more important than dtsbf. but if i fail to solve my problems because i lack executive functioning skills (plan, review, learn). how can i prioritize the corresponding solving recurrent tasks. i mean if i don't deep work enough because i don't proactively solve problems , i can' log this cause. if i can't solve all the nodes because i don't proactively solve problems, these skills tasks should be the most frequent.
        \item Fuck unified root cause analysis tree because the day i solve my trunc problem, eg deep work enough, the system will not solve anything therefore the proactive living skills will allow me to get back to achieving another thing and take care of myself.
        \item What if i do a trunc problem per life domain
        \begin{itemize}
            \item i am not living healthy enough
            \item i am not progressing my career
            \item i am not satisfied with relationships
            \item my entertainment is not good
            \item i have expad problems
            \item i have mental capacity problems
            \item i have mental skills problems
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{document}