\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\title{After crossing one per category}
\begin{document}
\maketitle
Now what?
\section{Introduction}
After having crossed one finish per daily category, what should I do?
\section{Current week selection}
I remember that current week, i should keep rotating thinking tasks, aka, progress on readings, progress on thinking docs, since last week's after minis selection is problems reports. I changed from problems reports into problems + reading because i can solve problems and anticipate problems alternatively.
\section{Next week's after minis}
I know it's not the time yet to analyse and decide, but this is a preparation since not too much available time sunday. Also, i like to prepare my options in order to make the decision in sunday instead of listing them in sunday.
\subsection{What should i choose next week}
\subsubsection{Déjà, zooming contraint}
Should i keep following zooming in zooming out pivots only? Why?
\subsubsection{If yes, what pivot}
\begin{itemize}
    \item no pivot: keep rotating two tasks, since unmastered yet
    \item zoom in
    \begin{itemize}
        \item on notes updating, since ideas foggy
        \item on ideas discovery, since i want to anticipate skills
    \end{itemize}
    \item zoom out: repeat one task per category after finish the first one per category. since i have urgency in all categories and since i want to start zooming in job search tasks.
\end{itemize}
\end{document}