\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\title{Notes organization}
\begin{document}
\maketitle
\section{Related problems}
\begin{itemize}
	\item I use many apps: word, obsidian, and now texstudio.
	\item Word lacks files navigation, Osidian lacks formatting, TexStudio can't open a folder.
\end{itemize}
\section{Facts} Since a skill is mastering a type of tasks, knowledge should be organized according to tasks. You should write for each problem an analysis article. It allows you a high level of thoughts clarity, and leaving a consultable record of the logic of decisions.
\section{Latex}
Why am i using latex? I am spending too much time configuring it, instead of learning actual skills.
\begin{itemize}
	\item An editor that allow me to open notes folder parallely. I could have just opened file explorer parallely to word.
	\item Better formatting than obsidian. I could have just used Word.
	\item I needed to zoom in zoom out while working on the document. Word does this.
	\item decomposition of one pdf project into multiple notes files like this \textbackslash input\{ conclusion.tex\}. why do i need this. If i remember it this might be useful \textrightarrow skills hierarchy decomposition principle. I am not using the functionality of which i based my pivot to latex upon.
\end{itemize}
\section{Whys}
\begin{itemize}
	\item Why have I a collections of writings
	\item Why is it organized the way it is?
	\item Should every folder represent a life goal by holding related notes?
	\item If yes, should every folder have a RCAT document?
\end{itemize}
\end{document}
