\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\title{How to get back to updating RCATs}
\begin{document}
\maketitle
I decided that the most important is returning to think using RCAT.
\section{Why}
Without a RCAT, I get a
    \begin{itemize}
        \item Loss feeling: i don't know what i want and what i need to do to get there.
        \item No pivot strategy to solve the deepest causes first.
    \end{itemize}
\section{Why can't I start RCAT maintenance?}
    \begin{itemize}
        \item thinking branch forgetting. Last time, problems kept growing  despite being productive. In what branch will you put proactive problem solving.
        \begin{itemize}
            \item cause of failing deep work
            \item cause of failing one of deep work root causes
            \item another trunc since if no proactive problem solving, there is no RCAT. 
        \end{itemize}
        \item managing the relationships between goals without culttering my analysis tree. For example, lack of self care cause DTSBF which cause deep work failure. My daily goals are a set of self care, dw tasks, addictions refusing to achieve my real goal of a quantity of deep work. And deep work is one solution among others to solve my other problems. I just got lost. Trying to link everything is wrong. Analyzing problems separatly is hard for me. Analyzing too many problems in the same day is the definition of having too many goals.
        \item if this is node, do i have root causes of failing to prevent and solve problems?
        \item Just by asking chatgpt and checking his answers, i discovered that i lack important skills practicing and knowledge like: executive functioning, self regulation, self care science, behavior change science, life skills, self management.
        \item I discovered that inefficient problem solving and preventing have causes but what does it cause in my unified rcat.
        \item it does not have to be in one rcat. i can grow a second tree now: a meta tree.
        \item The problem with starting a second tree is that i don't know how to prioritize tasks anymore.
        \item When i made no self care and rahp causing dtsbf wich causes failure to deep work i struggled to prioritize dtsbf vs FI. logging helped prioritized.
        \item how can i find the priority between dw and proactive living? is proactive living a cross rcat nodes problem
        \item i had a root cause analysis tree wich helped me prioritize tasks. i fail to deep work enough because i have family interruptions because i can't move out because i overspend and because i don't have job because i don't have technical skills. i have another branch: i don't deep work enough because i have frequent daytime sleepiness and  brainfog because i have too much addictions and i don't self care. logging the causes of failing deep work allowed to understand that family interruptions is more important than dtsbf. but if i fail to solve my problems because i lack executive functioning skills (plan, review, learn). how can i prioritize the corresponding solving recurrent tasks. i mean if i don't deep work enough because i don't proactively solve problems , i can' log this cause. if i can't solve all the nodes because i don't proactively solve problems, these skills tasks should be the most frequent.
        \item Fuck unified root cause analysis tree because the day i solve my trunc problem, eg deep work enough, the system will not solve anything therefore the proactive living skills will allow me to get back to achieving another thing and take care of myself.
        \item What if i do a trunc problem per life domain
        \begin{itemize}
            \item i am not living healthy enough
            \item i am not progressing my career
            \item i am not satisfied with relationships
            \item my entertainment is not good
            \item i have expad problems
            \item i have mental capacity problems
            \item i have mental skills problems
        \end{itemize}
    \end{itemize}
\section{Solutions}
\begin{itemize}
    \item don't recreate organization from scratch
    \item implement different frequencies logical finishes. But i already do it with after minis
\end{itemize}
Is it wrong to ask why am i failing this goal? Why do i have this problem? I mean maybe it is better to frequently ask this instead. What is the root cause that can explain some of my problems? 
\end{document}