\documentclass[12pt]{article}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{hyperref}
\title{Thinking problems}
\begin{document}
\maketitle
Most of my problems have known solutions. You don't have skills there are masters or small accomplishments. You don't have a job, create a pipeline. You overspend, create a budget. You have addictions, take the time to quit them. You have toxic relationships, cut them.
\section{So why am i not solving concrete problems}
\subsection{I am afraid of solving because it brought me here}
\subsection{Prioritizing my problems is painful and tiresome}
\subsection{I don't postpone solutions maintenance}
\subsection{I don't have guidance, feedback and related literature}
\subsection{I don' work to concrete milestones}
\subsection{I don't maintain a plan}
\section{What should i do?}
\begin{itemize}
    \item make a 10 step plan
    \item each step should be doable in under 45 minutes
    \item the last step is make a 10 step plan: this i failed.
\end{itemize}
Something has got to give. I need to change something. My thinking/ time spending/ organization needs to change. I wish i can figure it out. What if describing how i spend my time, the most important problem and solving it is my mission.
\begin{itemize}
    \item stop writing
    \item stop solving problems
    \item stop thinking
    \item stop deep working
    \item stop spending time without day plan
    \item stop trying to do anything without RAHP
    \item stop doing anything before repeating simple steps.
    \item stop living without long term plan
\end{itemize}
Problems keep resurfacing
•	This problem is true but I don’t remember them (maybe not important then)
Graver problems keep coming
•	I regret not making decisions according to my 15/16/17/18 goals (stability, socialization, independence, awalt
•	I don’t anticipate preventable problems like ( any current one)
problems interconnection
•	I lack system orientation per deep work subtask (aka the items inside main DW activities).
o	It does not have to be units’ management but applying steps on inputs into outputs.
o	another solution to problems interconnection is work system coupling
•	I keep wishing I reintroduce RCAT despite problems interconnection.
•	I don’t understand the relationships between thinking, learning and execution
•	Problem report template lacks a causes analysis and addressing

\end{document}